---
title: "SMART Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
    theme: cosmo
    logo: michigan-logo.png
    favicon: michigan-logo.png
vertical_layout: fill
runtime: shiny
---

<style>
.navbar-logo.pull-left {
  padding-top:4px;
}
.navbar {
  background-color:#003D79;
  border-color:white;
}
.navbar-brand {
color:white!important;
}
</style>   

<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 15px

</style>

```{r setup, include=FALSE}
# packages
library(flexdashboard)
library(shiny)
library(plotly)
library(ggiraph)
library(ggiraphExtra)
library(RColorBrewer)
library(stringr)
library(shinythemes)
library(shinyTime)
library(DT)
library(data.table)
library(highcharter)
library(waffle)

# data and functions
source('redcap-data.R')
source('functions.R')
```

Screening & Enrollment
========================================================================

Row {data-height=30%}
------------------------------------------------------------------------

### Enrolled

```{r}

valueBox(
  value = sprintf('%i (%.0f%%)', test_enrolledCount, test_enrolledRate * 100), 
  caption = sprintf('enrolled as of %s', format(Sys.Date(), '%B %d, %Y')), 
  color = 'lightgreen', 
  icon = 'ion-android-checkbox-outline'
)

```

### Exclusions due to Eligibility

```{r}

valueBox(
  value = sprintf('%i (%.0f%%)', test_excludedEligibility, test_excludedEligibilityRate * 100),
  caption = 'excluded due to eligilibity requirements', 
  color = 'orange', 
  icon = 'ion-ios-flag'
)
  
```

### Exclusions due to Informed Consent Refusal

```{r}

valueBox(
  value = sprintf('%i (%.0f%%)', test_excludedIC, test_excludedICRate * 100),
  caption = 'refused informed consent', 
  color = 'orange', 
  icon = 'ion-android-clipboard'
)
  
```

Row {data-height=70%}
------------------------------------------------------------------------

### Reasons for Exclusion {data-width=50%}

```{r}

tm_data <- data_to_hierarchical(
  data = test_exclusionData, 
  group_vars = c(reason_class, reason), 
  size_var = count, 
  colors = rev(brewer.pal(n = 6, name = 'Blues'))
)

hchart(
  tm_data, 
  type = 'treemap'
)

```

### Patient Enrollment by Month {data-width=50%}

```{r}

enrollment_plot <- ggplot(data = test_monthlyEnrollment, aes(fill = type)) + 
  geom_bar(aes(x = month, y = count, group = type), 
           stat = 'identity', 
           position = position_dodge(0.9), 
           color = 'black'
  ) + 
  scale_fill_brewer(palette = 'Greens') + 
  xlab('') + ylab('') + 
  theme_bw() + 
  theme(
    legend.position = 'none'
  )

ggplotly(enrollment_plot, tooltip = c('x', 'group', 'y'))

```

Treatment Assignment
========================================================================

### Patient Assignment 

```{r}

assign_ui <- fluidPage(
  br(''), 
  # sidebar
  sidebarLayout(
    # randomization
    sidebarPanel(
      title = 'Inputs',
      textInput(
        inputId = 'patient_id', 
        label = 'Patient ID'
      ),
      checkboxInput(
        inputId = 'second_treatment', 
        label = 'Stage 2', 
      ), 
      actionButton(
        inputId = 'submit', 
        label = 'Show Assignment')
    ), 
    # show current data
    mainPanel(
      dataTableOutput('responses')
    )
  )
)

assign_server <- function(input, output, session) {
  
  # input
  id <- eventReactive(input$submit, input$patient_id)
  treat2 <- eventReactive(input$submit, input$second_treatment)
  
  # retrieve row of interest
  getRow <- reactive({
    reveal_row(id(), treat2())
  })
  
  # save row to output
  output$responses <- renderDataTable(
    {input$submit
    datatable(
      getRow(), 
      colnames = c('ID', 'Stage 1', 'Stage 2'), 
      rownames = FALSE, 
      options = list(
        paging = FALSE, 
        dom = 't'
      )
    )}
  )

}

shinyApp(
  ui = assign_ui, 
  server = assign_server
)

```

### Treatment Distribution as of `r format(Sys.Date(), "%B %d, %Y")`

```{r}

test <- test_treatment %>%
  mutate(
    treatment_one = case_when(
      treatment_one == 'Upadacitinib 30mg BID' ~ 'Upa', 
      treatment_one == 'IV Methylprednisolone 30mg BID + Upadacitinib 45mg daily' ~ 'Methylpred + Upa', 
      treatment_one == 'IV Methylprednisolone 30mg BID' ~ 'Methylpred'
    ), 
    treatment_two = case_when(
      treatment_two == 'Add IV Methylprednisolone 30mg BID' ~ 'Add Methylpred', 
      treatment_two == 'Add Upadacitinib 30mg BID Rescue' ~ 'Add Upa', 
      treatment_two == 'Escalate to IV Methylprednisolone 30mg BID + Upadacitinib 30mg BID' ~ 'Escalate', 
      treatment_two == 'Add Cyclosporine Rescue' ~ 'Add Cyclo', 
      treatment_two == 'Switch to Cyclosporine Rescue' ~ 'Switch to Cyclo', 
      treatment_two == 'Switch to IV Methylprednisolone 30mg BID + Cyclosporine' ~ 'Switch to Methylpred + Cyclo'
    ), 
    treatment_two = str_wrap(treatment_two, 15)
  )

treatment_plot <- custom_ggPieDonut(
    data = test, 
    mapping = aes(pies = treatment_one, donuts = treatment_two), 
    labelposition = 1, 
    palette = 'Set 1'
  )

ggiraph(code = print(treatment_plot))

```

Assessment Times
========================================================================

### Scheduled Date and Time of Patient Assessments

```{r}

assess_table <- datatable(
      assess_toDF(assessData), 
      rownames = FALSE, 
      colnames = c('ID', 'Treatment Start Time', '24 Hours', '48 Hours', '72 Hours'), 
      options = list(
        dom = 'ft', 
        columnDefs = list(list(visible=FALSE, targets=c(5:7))), 
        pageLength = 1000
      )
    ) %>% 
    formatDate(~start_time + day_one + day_two + day_three, method = 'toLocaleString') %>%
    formatStyle(
      'day_one', 
      'time_until_day_one', 
      backgroundColor = styleInterval(c(-6, 6), c('white', 'red', 'white'))
    ) %>% 
    formatStyle(
      'day_two',
      'time_until_day_two', 
      backgroundColor = styleInterval(c(-6, 6), c('white', 'red', 'white'))
    ) %>%
    formatStyle(
      'day_three', 
      'time_until_day_three', 
      backgroundColor = styleInterval(c(-6, 6), c('white', 'red', 'white'))
    )

renderDataTable(assess_table)

```

Results
========================================================================

Row
------------------------------------------------------------------------

### CRP Tracker

```{r}
    
symptom_plot <- test_snr %>%
  pivot_longer(cols = contains('day'), names_to = 'time', values_to = 'CRP') %>%
  mutate(
    stage = ifelse(stage == 1, 'Stage 1', 'Stage 2'), 
    time = case_when(
      time == 'day0' ~ 'Day 0',
      time == 'day1' ~ 'Day 1', 
      time == 'day2' ~ 'Day 2', 
      time == 'day3' ~ 'Day 3'
    )
  ) %>%
  ggplot(aes(x = time, y = CRP, group = PatientID, color = as.factor(PatientID))) + 
  facet_wrap(~as.factor(stage)) + 
  geom_line() + 
  geom_point() + 
  scale_y_continuous(breaks = c(2.5, 5, 7.5, 10, 12.5)) + 
  theme_bw() + 
  labs(color = 'Patient ID') + 
  xlab('')

gg <- ggplotly(symptom_plot)

gg <- plotly_build(gg) 

for(i in 3:nrow(test_snr)){
  gg$x$data[[i]]$visible <- 'legendonly'
}

gg
    

```

Row
------------------------------------------------------------------------

### Outcomes by Treatment {data-width=60%}

```{r}

response_table <- test_snr %>%
    select(PatientID, stage, treatment, response) %>%
    filter(stage == 1) %>%
    group_by(treatment) %>%
    summarize(
      Responders = sum(response == 'Y'), 
      'Non-Responders' = sum(response == 'N'), 
      'In-Progress' = sum(response == 'U'), 
      Total = n(), 
      'Response Rate' = round(Responders/Total*100, 2)
    ) %>%
  rename(Treatment = treatment)

renderDataTable(
  response_table, 
  rownames = FALSE, 
  options = list(
    paging = FALSE, 
    searching = FALSE, 
    dom = 't'
  )
)

```

### Stage 1 Summary {data-width=20%}

```{r}

hchart(
  test_responseData1, 
  type = 'item', 
  hcaes(name = response_status, y = value)
) %>%
  hc_colors(colors = c('lightgreen', 'skyblue', 'red'))

```

### Stage 2 Summary {data-width=20%}

```{r}

hchart(
  test_responseData2, 
  type = 'item', 
  hcaes(name = response_status, y = value)
) %>%
  hc_colors(colors = c('lightgreen', 'skyblue', 'red'))

```

